Real-time resolving assembly graph by ONT long reads data

### 2019-11-19 paper.tex
fsdf

Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph. 
A modified DFS (depth-first search) algorithm and a progressive voting algorithm has been implemented to overcome these issues.
This results in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g. \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed. These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

@@

In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity. The assembler was able to handle the De Bruijin assembly graph from Illumina data generated by $\mathtt{metaSPAdes}$ and simplify it using a minimal input stream of long reads. 
The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference. The issue is reasoned by the insufficient short-read input to cover underpresented species in the mixture, especially in the case of Log community.
As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly. The algorithm operates on the assumption of a high quality assembly from sufficient Illumina data that produces decent assembly graph, with a minimal amount of long reads data possible. A fragmented initial graph directly affects the quality of the final assembly, free from the abundance of nanopore data.

%metagenomics attempt, how to improve?

>>>>

Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph. 
A modified DFS (depth-first search) algorithm and a progressive voting algorithm has been implemented to overcome these issues.
The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g. \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed. These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

@@

In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity. The assembler was able to handle the De Bruijin assembly graph from Illumina data generated by $\mathtt{metaSPAdes}$ and simplify it using a minimal input stream of long reads. 
The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference. The issue is caused by the shortage of short-read sequencing input to cover underpresented species in the mixture, especially for the Log community.

As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly. The algorithm operates on the assumption of a high quality assembly from a well-supplied source of short-read data for a decent assembly graph to begin with.
It then consumes a just-enought amount of data from a streaming input of nanopore reads to resolve the graph. 
In summary, extra pre-processing and comprehensive binning for the initial graph could further improve the performance of \npgraph{}.
